### 2020-06-14 report/sections/server/codegen/testing.tex
Report: minor fix

As the generated TypeScript code makes assumptions about the
environment in which it is used (for example, having the \texttt{ws}
WebSocket package installed on server-side endpoints), we require a
sandbox environment to type-check the generated code. 
The sandbox contains the minimal boilerplate required
for testing -- this involves having the WebSocket package installed
for server-side endpoints, the React.js framework (\cref{section:react})
instantiated for browser-side endpoints,
and corresponding \texttt{tsconfig.json} files for both targets to
be picked up by the TypeScript Compiler.

>>>>

As the generated TypeScript code makes assumptions about the
environment in which it is used (for example, having the \texttt{ws}
WebSocket package installed on server-side endpoints), we require a
sandbox environment to type-check the generated code. 
The sandbox contains the minimal boilerplate required
for testing -- this involves having the WebSocket package installed
for server-side endpoints, the React.js framework (\cref{chap:react})
instantiated for browser-side endpoints,
and corresponding \texttt{tsconfig.json} files for both targets to
be picked up by the TypeScript Compiler.
